### 2023-12-26 globals/metadata.tex
looking again

\title{Title of the document}
\author{Author of the document}
\date{\today}
\bibliography{globals/papers}

\newcommand{\acknowledge}{
    Acknowledge
}

\newcommand{\makeabstract}{
    \begin{abstract}
        Abstract of the paper.
    \end{abstract}
}

>>>>

\title{A corrected version of Karhumäki’s theorem
       on commutative polynomial $\Nat$-rational series}
\author{
    Lopez Aliaume
}
\date{\today}
\bibliography{globals/papers}

\newcommand{\acknowledge}{
    I would like to thank Gaëtan Douéneau-Tabot
    for mentionning this problem, checking 
    my counter-example, and supporting me in publishing
    this paper.
}

\newcommand{\makeabstract}{
    \begin{abstract}
        Deciding whether a $\Rel$-rational series
        can be computed as a $\Nat$-rational series
        is an open problem that was solved by Karhumäki in the
        specific case of $\Rel$-rational series that are commutative
        and compute a polynomial.
        We propose a short counter-example to this
        previous result on commutative $\Nat$-rational series,
        and prove a corrected version of the theorem, that only
        requires commutativity and a polynomial growth rate.
        We then discuss how the syntactic criterion could
        pave the way towards a decision procedure when the commutativity
        of the $\Rel$-rational series
        is not assumed.
    \end{abstract}
}

### 2023-12-26 pnrs.tex
looking again

Let us first state the result 
of \citeauthor{KARH77}, in terms of its
class $\CoveredPoly$ of polynomials defined as follows:
\begin{definition}[{\cite[Section 3, page 3]{KARH77}}]
    Let $\vec{X}$ be a finite tuple of indeterminate.
    The class $\CoveredPoly[\vec{X}]$
    is the class of polynomials $P \in \Rel[\vec{X}]$
    that are \kl{non-negative}
    and such that every \kl{maximal monomial} has a \kl{positive coefficient}.
    When the indeterminate are clear from the context, we write
    this class $\CoveredPoly$.
\end{definition}

@@

\paragraph*{Context.}
There has been recent interest in $\Rel$ and $\Nat$-rational series exhibiting
\emph{polynomial growth} \cite{doueneau2021pebble,bojanczyk2022transducers}.
This computational model, in the counting case, can be traced back to a model
introduced by \textcite{schutzenberger1965finite}. It has been recently proven
that one can decide the growth rate of such functions, and decide whether they
are aperiodic in the case of $\Rel$-rational series \cite{LOPEZ23b}. It was
conjectured in the PhD thesis of one of the authors, that the membership
problem of $\Nat$-rational series among $\Rel$-rational series was decidable
under the assumption of polynomial growth. This conjecture was based on a
result of \textcite{KARH77}, which we will disprove in \cref{sec:c-example}. We
then provide in \cref{sec:proof} a corrected version of the theorem, together
with a valid proof. As a consequence, it does not invalidate the stated
conjecture.

\AP
\paragraph*{Rational series and regular languages.}
\begin{fact}
    The language $\setof{ w \in \Sigma}{ \card[a]{w} = \card[b]{w}}$
    is not regular.
\end{fact}

\begin{fact}
    regular languages are closed under intersections.
\end{fact}

TODO.

clasical results from \cite{berstel2011noncommutative}.
\begin{fact}
    \label{pre-image-regular:fact}
    The pre-image of a regular language by a $\Nat$-rational series
    is a regular language.
\end{fact}

\begin{fact}
    \label{polynomial-rational-polyreg:fact}
    polynomial + rational = unary polyregular.
\end{fact}

\AP
\paragraph*{Polynomials.}
Before stating the result, let us introduce the necessary vocabulary on
rational series, together with concrete examples so that no doubt is allowed as
to their meaning. A $\Rel$-rational series $f \colon \Sigma \to \Rel$ is
\intro{commutative} whenever $f(uv) = f(vu)$ for all $u,v \in \Sigma^*$. A
polynomial $P \in \Rel[\seqof{X_a}{a \in \Sigma}]$ is a \intro{$\Rel$-rational
polynomial} if there exists a \reintro{commutative} $\Rel$-rational series $f$
such that $f(w) = P(\seqof{ \card[a]{w} }{a \in \Sigma})$. Similarly, a
\intro{$\Nat$-rational polynomial} if the \reintro{commutative} $\Rel$-rational
series is in fact $\Nat$-rational.

\begin{example}
    \label{negative-not-nrat:ex}
    With $\Sigma \defined \set{1}$,
    the polynomials $X_1$, and $X_1^2 + 3$ are \kl{$\Nat$-rational polynomial},
    but $- X_1$ is a \kl{$\Rel$-rational polynomial} that is 
    not a \kl{$\Nat$-rational polynomial}.
\end{example}
\begin{proof}
    TODO:
    The polynomial $X_1$ is computed by the rational series,
    the polynomial $X_1^2 + 3$ is computed by,
    and the polynomial
    $- X_1$ cannot be $\Nat$-rational as $\Nat$-rational series
    have non-negative output.
\end{proof}

@@

\begin{example}
    Over a binary alphabet $\Sigma \defined \set{a,b}$,
    the polynomial $P(X_a, X_b) \defined (X_a - X_b)^2$
    is a \kl{$\Rel$-rational polynomial} that is \kl{non-negative},
    but is
    not a \kl{$\Nat$-rational polynomial}.
\end{example}
\begin{proof}
    Assume by contradiction that
    $S$ is a $\Nat$-rational series computing $P$.
    Then, $S^{-1}(\set{0})$ should be a regular language
    (\cref{pre-image-regular:fact}),
    but $S^{-1}(\set{0}) = \setof{ w \in \Sigma }{ \card[a]{w} = \card[b]{w} }$
    is not a regular languge.
\end{proof}

\AP Let us now give some vocabulary on polynomials with multiple indeterminate
over $\Rel$. 
A \intro{monomial} is a product of variables and integers.
\begin{example}
    $XY$ is a \kl{monomial}, $3 X$ is a \kl{monomial}, 
    but $X + Y$ or $2X^2 + XY$ are not.
\end{example}
A polynomial $P \in \Rel[X_1, \dots, X_k]$ is \intro{non-negative}
if $P(n_1, \dots, n_k) \geq 0$ for all $n_1, \dots, n_k \geq 0$. Beware that we
do not consider negative values, as the numbers $n_i$ will ultimately count the
number of occurrences of a letter in a word.
\begin{example}
    The polynomial $(X - Y)^2$ is \kl{non-negative},
    and so is the polynomial $X^3$, but the polynomial
    $X^2 - 2X$ is not.
\end{example}
In a polynomial $P \in \Rel[X_1, \dots, X_k]$, a monomial 
is a \intro{maximal monomial} if it is a maximal element
for the visibility ordering of polynomials \emph{in $\Rat$}
among monomials with non-zero coefficients in $P$.\footnote{
    One could equivalently define maximal elements by removing the (non-zero)
    multiplicative constant of the monomials, and then
    considering the usual divisibility relation of $\Rel$ polynomials.
}
\begin{example}
    In the polynomial 
    $P(X,Y) \defined X^2 - 2XY + X^2 + X + Y$, the \reintro{maximal monomials}
    are $X^2$, $-2 XY$, and $X^2$.
\end{example}
A \kl{monomial} has \intro{positive coefficient} in a polynomial $P$
if its multiplicative constant is positive.
\begin{example}
    In the polynomial $P(X,Y) \defined (X - Y)^2$, 
    the \kl{positive monomials} are
    $X^2$ and $Y^2$.
\end{example}

@@

Let us now introduce the counter example that was found trying to
replicate the original proof. Notice that the counter example
will use three indeterminate, because we will prove
in \cref{sec:proof} that \citeauthor{KARH77}’s theorem holds
on polynomial with at most two indeterminate.

@@

    Now, let us consider the language $L \defined \setof{w}{ f(w) = 0}$. By the
    above computation, we conclude that $L = \setof{ w \in \set{a,b}^* }{
    \card[a]{w} = \card[b]{w} } \cup \set{ c }^*$.
    Because $L \cap \set{a,b}^*$ is notoriously not a regular language, we
    conclude that $L$ is not a regular language.
    However, $L = f^{-1}(\set{0})$, which is a regular language
    because $f$ is a $\Nat$-rational series
    (\cref{pre-image-regular:fact}).
\end{proof}

@@

Let us now provide another class of polynomials, $\CorrectPoly$. The definition
will involve fixing the value of indeterminate, for which we use the following
notation: $\restr{P(X,Y)}{X = 1}$ is the polynomial $P(1,Y)$. More generally,
if $\nu$ is a partial function from $\vec{X}$ to $\Nat$, the restriction
$\restr{P(\vec{X})}{\nu}$ is the polynomial with indeterminate $\vec{Y}
\defined \vec{X} - \dom(\nu)$ obtained by fixing the variables of the
domain of $\nu$.

@@

First, let us remark that $\CorrectPoly \subseteq \CoveredPoly$, because
polynomials in $\CorrectPoly$ are \kl{non-negative}.

Before proving that $\CorrectPoly$ captures \kl{$\Nat$-rational polynomials},
let us first check that the counter example provided in
\cref{thm:counter-example} is not in $\CorrectPoly$. For that, notice that for
$P$ defined in \cref{def:bad-polynomial}, $P(X,Y,1) = 3X^2 + 3Y^2 - 2XY$, which
has a negative coefficient for a \kl{maximal monomial}, namely $-2XY$.

Let us now prove that \kl{$\Nat$-rational polynomials} are
in $\CorrectPoly$.
To simplify the reasoning, we will use results on $\Nat$-polyregular
functions, also known as, polyregular functions with unary output.

\begin{lemma}
    The \kl{$\Nat$-rational polynomials} are in $\CorrectPoly$.
\end{lemma}
\begin{proof}[Proof Idea]
    Let $P$ be a \kl{$\Nat$-rational polynomial}.
    Let $\Sigma$  be the finite alphabet such that
    $P \in \Rel[\seqof{X_a}{a \in \Sigma}]$,
    and $f \colon \Sigma^* \to \Nat$ be the \kl{commutative}
    $\Nat$-rational series computing $P$.
    Because $f$ has polynomial growth, and is a $\Nat$-rational series,
    it is a $\Nat$-polyregular function 
    (\cref{polynomial-rational-polyreg:fact}).
    In particular, 
    there exists a tuple $\vec{x}$ of free variables
    $\MSO$ formulas $\psi_1(\vec{x}), \dots, \psi_n(\vec{x})$,
    and positive coefficients $\alpha_1, \dots, \alpha_n \in \Nat$,
    such that
    \begin{equation*}
        f(w) = \left(\sum_{i = 1}^n \alpha_i \vcount{\psi_i}\right)(w) \quad .
    \end{equation*}

    \textbf{TODO: only look at words of the form $\prod_{a \in \Sigma} a^{k_a}$,
    because this is enough}.
    \textbf{TODO: this has positive maximal coefficients}.
    Furthermore, this remains true when restricting the language.
\end{proof}

@@

@@

@@

>>>>

We will start by formally stating the result of \citeauthor{KARH77}
in terms of polynomials and commutative $\Nat$-rational series, and
then introduce the necessary definitions. The characterization of
commutative $\Nat$-rational series computing polynomial functions
is described in terms of a class $\CoveredPoly[\vec{X}]$ of
polynomials with multiple indeterminate.

\begin{definition}[{\cite[Section 3, page 3]{KARH77}}]
    Let $\vec{X}$ be a finite tuple of indeterminate.
    The class $\CoveredPoly[\vec{X}]$
    is the class of polynomials $P \in \Rel[\vec{X}]$
    that are \kl{non-negative}
    and such that every \kl{maximal monomial} has a \kl{positive coefficient}.
    When the indeterminate are clear from the context, we write
    this class $\CoveredPoly$.
\end{definition}

We use the term \kl{$\Nat$-rational polynomial}, that will formally be
stated later on, to denote polynomials that can be computed via a
$\Nat$-rational series. In the upcoming theorem, this property
which is \emph{a priori} difficult to decide is reduced to 
the positivity of the polynomial, and the positivity of \emph{some}
coefficients.

@@

It is not clearly stated in \cite{KARH77}, but \cref{karh:thm} implies the
decidability of \kl{$\Nat$-rational polynomial} inside polynomials with $\Rel$
coefficients. We will not formalize this statement yet, as \cref{karh:thm}
does not hold in general.

\paragraph*{Context.} There has been recent interest in $\Rel$ and
$\Nat$-rational series exhibiting \emph{polynomial growth}
\cite{doueneau2021pebble,bojanczyk2022transducers}. This computational model,
in the counting case, can be traced back to a model introduced by
\textcite{schutzenberger1965finite}. It has been recently proven that one can
decide the growth rate of such functions, and decide whether they are aperiodic
in the case of $\Rel$-rational series \cite{LOPEZ23b}. It was conjectured in
the PhD thesis of Gaëtan Douéneau-Tabot, that the membership problem of
$\Nat$-rational series among $\Rel$-rational series was decidable under the
assumption of polynomial growth. This conjecture was based on the previously
introduced result of \textcite{KARH77} (\cref{karh:thm}), which we will
disprove in \cref{sec:c-example}. We then provide in \cref{sec:proof} a
corrected version of the theorem, together with a valid proof. As a
consequence, it does not invalidate the stated conjecture.

\begin{itemize}
    \item commutative input and output
    \item commutative output
    \item no commutativity ?
\end{itemize}

\AP \paragraph*{Rational series and regular languages.} This paper uses notions
of regularity and results about \kl{$\Nat$-rational series}, however most of
the technicalities will stem from the multiple indeterminate of polynomials,
and all there is to know about regularity in this document will be confined to
the following facts. For a survey about (non-commutative) rational series, we
refer the reader to \cite{berstel2011noncommutative}.

\begin{definition}[Rational series]
    The following are equivalent
    \begin{itemize}
        \item weighted automata
        \item rational expressions
        \item 
    \end{itemize}
\end{definition}

\begin{definition}[Commutative rational series]
    A $\Rel$-rational series
    $f \colon \Sigma \to \Rel$ is \intro{commutative} whenever $f(uv) = f(vu)$ for
    all $u,v \in \Sigma^*$.
\end{definition}

\begin{fact}[Folklore about regular languages]
    \label{regular:fact}
    The language $\setof{ w \in \Sigma}{ \card[a]{w} = \card[b]{w}}$
    is not regular, whenever $a,b \in \Sigma$.
    Regular languages are closed under intersection.
\end{fact}

\begin{fact}
    \label{pre-image-regular:fact}
    The pre-image of a regular language by a $\Nat$-rational series
    is a regular language. In particular,
    for all $\Nat$-rational series $S$, $S^{-1}(\set{0})$ is a regular
    language.
\end{fact}

\AP \paragraph*{Polynomials.} All polynomials considered in this paper have
coefficients in $\Rel$ unless explicitly stated otherwise. A polynomial $P \in
\Rel[\seqof{X_a}{a \in \Sigma}]$ is a \intro{$\Rel$-rational polynomial} if
there exists a \reintro{commutative} $\Rel$-rational series $f$ such that $f(w)
= P(\seqof{ \card[a]{w} }{a \in \Sigma})$. Similarly, $P$ is a
\intro{$\Nat$-rational polynomial} if the \reintro{commutative} $\Rel$-rational
series is in fact $\Nat$-rational. Beware that we only apply the polynomial
to \emph{non-negative} values.

\begin{example}
    \label{negative-not-nrat:ex}
    With $\Sigma \defined \set{1}$,
    the polynomials $X_1$, and $X_1^2 + 3$ are \kl{$\Nat$-rational polynomial},
    but $- X_1$ is a \kl{$\Rel$-rational polynomial} that is 
    not a \kl{$\Nat$-rational polynomial}.
\end{example}
\begin{proof}
    The function $w \mapsto |w|$ is a \kl{polyregular function} with unary
    output of \kl{polynomial growth}, hence  can be computed by a
    \kl{$\Nat$-rational series}. Hence, $P(X_1) \defined X_1$ is
    a \kl{$\Nat$-rational polynomial}. Similarly,
    $w \mapsto |w|^2 + 3$ is a \kl{$\Nat$-rational series},
    showing that $Q(X_1) \defined X_1^2 + 3$
    is a \kl{$\Nat$-rational polynomial}.
    Finally, 
    $T(X_1) \defined - X_1$ cannot be $\Nat$-rational as $\Nat$-rational series
    have non-negative output.
\end{proof}

@@

\begin{example}
    Over a binary alphabet $\Sigma \defined \set{a,b}$,
    the polynomial $P(X_a, X_b) \defined (X_a - X_b)^2$
    is a \kl{$\Rel$-rational polynomial} that is \kl{non-negative},
    but is
    not a \kl{$\Nat$-rational polynomial}.
\end{example}
\begin{proof}
    Assume by contradiction that
    $S$ is a $\Nat$-rational series computing $P$.
    Then, $S^{-1}(\set{0})$ should be a regular language
    (\cref{pre-image-regular:fact}),
    but $S^{-1}(\set{0}) = \setof{ w \in \Sigma }{ \card[a]{w} = \card[b]{w} }$
    is not a regular language (\cref{regular:fact}).
\end{proof}

\AP Let us now give some vocabulary on polynomials with multiple indeterminate
over $\Rel$. A \intro{monomial} is a product of variables and integers. For
instance, $XY$ is a \kl{monomial}, $3 X$ is a \kl{monomial}, but $X + Y$ or
$2X^2 + XY$ are not.

\AP A polynomial $P \in \Rel[X_1, \dots, X_k]$ is \intro{non-negative} if
$P(n_1, \dots, n_k) \geq 0$ for all $n_1, \dots, n_k \geq 0$. Beware that we do
not consider negative values, as the numbers $n_i$ will ultimately count the
number of occurrences of a letter in a word. As an example, the polynomial $(X
- Y)^2$ is \kl{non-negative}, and so is the polynomial $X^3$, but the
polynomial $X^2 - 2X$ is not.

\AP
In a polynomial $P \in \Rel[X_1, \dots, X_k]$, a monomial 
is a \intro{maximal monomial} if it is a maximal element
for the visibility ordering of polynomials \emph{in $\Rat$}
among monomials with non-zero coefficients in $P$.\footnote{
    One could equivalently define maximal elements by removing the (non-zero)
    multiplicative constant of the monomials, and then
    considering the usual divisibility relation of $\Rel$ polynomials.
}
In the polynomial 
$P(X,Y) \defined X^2 - 2XY + X^2 + X + Y$, the \reintro{maximal monomials}
are $X^2$, $-2 XY$, and $X^2$.
A \kl{monomial} has \intro{positive coefficient} in a polynomial $P$ if its
multiplicative constant is positive. In the polynomial $P(X,Y) \defined (X -
Y)^2$, the \kl{positive monomials} are $X^2$ and $Y^2$.

\paragraph*{Outline of the paper.}
todo.

@@

Let us now introduce the counter example that was found trying to generalise
the original proof to non-commutative \kl{$\Rel$-rational series} of
\kl{polynomial growth}. The counter example will use three indeterminate, and
we will prove in \cref{sec:proof} that \citeauthor{KARH77}’s theorem holds on
polynomial with at most two indeterminate.

@@

    Now, let us consider the language $L \defined \setof{w}{ f(w) = 0}$. By the
    above computation, we conclude that $L = \setof{ w \in \set{a,b}^* }{
    \card[a]{w} = \card[b]{w} } \cup \set{ c }^*$.
    Because $L \cap \set{a,b}^*$ is notoriously not a regular language
    (\cref{regular:fact}), we
    conclude that $L$ is not a regular language.
    However, $L = f^{-1}(\set{0})$, which is a regular language
    because $f$ is a $\Nat$-rational series
    (\cref{pre-image-regular:fact}).
\end{proof}

@@

Let us now provide another class of polynomials, $\CorrectPoly$, that restricts
$\CoveredPoly$ to a subset that is ``closed under fixing indeterminate", namely,
polynomials $P(X_1, \dots, X_n) \in \CoveredPoly$ such that partially evaluated
polynomials remain in $\CoveredPoly$. We use the following notation
to fix the value of some indeterminate
$\intro*\restr{P(X,Y)}{X = 1}$ is the polynomial $P(1,Y)$. More generally, if $\nu$ is
a partial function from $\vec{X}$ to $\Nat$, the restriction
$\restr{P(\vec{X})}{\nu}$ is the polynomial with indeterminate $\vec{Y}
\defined \vec{X} - \dom(\nu)$ obtained by fixing the variables of the domain of
$\nu$.

@@

First, let us remark that $\CorrectPoly \subseteq \CoveredPoly$, because
polynomials in $\CorrectPoly$ are \kl{non-negative}. Let us also check that the
counter example provided in \cref{thm:counter-example} is not in
$\CorrectPoly$. For that, notice that for $P$ defined in
\cref{def:bad-polynomial}, $P(X,Y,1) = 3X^2 + 3Y^2 - 2XY$, which has a negative
coefficient for a \kl{maximal monomial}, namely $-2XY$.

Let us now prove that \kl{$\Nat$-rational polynomials} are in $\CorrectPoly$.
To simplify the reasoning, we will use results on $\Nat$-polyregular functions,
also known as, polyregular functions with unary output
\cite{doueneau2021pebble,bojanczyk2019string}. Note that the connection between
rational series and polyregular functions is not specific to $\Nat$, as
$\Rel$-rational series of polynomial growth are computed as polyregular
functions with output in $\set{+1,-1}$ post-composed with computing the sum of
outputted letters \cite{LOPEZ23b}. Because we only consider functions with
output in $\Rel$, and that a commutative output monoid simplifies the definitions,
let us only define $\Rel$-polyregular functions.

\begin{definition}[$\Rel$-polyregular functions, {\cite[see, e.g.]{LOPEZ23b}}]
    Let $M$ be a finite monoid, $\mu \colon \Sigma^* \to M$
    be a morphism, $k \in \Nat$, and 
    $\pi \colon M^k \to \Rel$ be a production function.
    The \intro{$\Rel$-polyregular function}
    $\pi^\dagger \colon \Sigma^* \to \Rel$
    is computed as follows:
    \begin{equation*}
        f(w) \defined
        \sum_{w = u_1 \cdots u_k} \pi(\mu(u_1), \dots, \mu(u_k))
        \quad .
    \end{equation*}

    When $\pi$ has co-domain $\Nat$, the function $\pi^\dagger$
    is called \intro{$\Nat$-polyregular}.
\end{definition}

\begin{fact}[see e.g. ...]
    \label{polynomial-rational-polyreg:fact}
    Let $\Sigma$ be a finite alphabet, and $f \colon \Sigma^* \to \Nat$
    be a function. The following are equivalent:
    \begin{enumerate}
        \item $f$ can be computed as a \k{$\Nat$-rational series}
            of \kl{polynomial growth}.
        \item $f$ is a \kl{$\Nat$-polyregular function}.
    \end{enumerate}
\end{fact}

@@

\begin{lemma}
    The \kl{$\Nat$-rational polynomials} are in $\CorrectPoly$.
\end{lemma}
\begin{proof}[Proof Idea]
    Let $P$ be a \kl{$\Nat$-rational polynomial}.
    Let $\Sigma$  be the finite alphabet such that
    $P \in \Rel[\seqof{X_a}{a \in \Sigma}]$,
    and $f \colon \Sigma^* \to \Nat$ be the \kl{commutative}
    $\Nat$-rational series computing $P$.
    Because $f$ has polynomial growth, and is a $\Nat$-rational series,
    it is a $\Nat$-polyregular function 
    (\cref{polynomial-rational-polyreg:fact}).
    In particular, 
    there exists a finite monoid $M$,
    a morphism $\mu \colon \Sigma^* \to M$,
    an integer $p  \in \Nat$,
    and a production function $\pi \colon M^p \to \Nat$,
    such that for all words $w \in \Sigma^*$,
    \begin{equation*}
        f(w) = \sum_{w = u_1 \cdots u_p} \pi(\mu(u_1), \dots, \mu(u_p)) \quad .
    \end{equation*}
    Because $f$ is \kl{commutative}, we can restrict our attention
    to words of the form $\prod_{a \in \Sigma} a^{k_a}$ to compute $f$.
    To that end, let us
    consider $\omega \in \Nat$ such that
    $m^\omega$ is an idempotent for all $m \in M$ (this is possible because
    $M$ is finite).
    Then, $f( \prod_{a \in \Sigma} a^{ \omega \times k_a} )$
    can be computed as follows:
    \begin{align*}
    f(\prod_{a \in \Sigma} a^{ \omega \times k_a} )
    &= 
    \sum_{\prod_{a \in \Sigma} a^{\omega \times k_a}
    = u_1 \cdots u_p} 
         \pi(\mu(u_1), \dots, \mu(u_p)) \\
    &= \pi(a^\omega, \dots, a^\omega) 
    \end{align*}
    is a polynomial in $k_a$, whose maximal coefficients are
    sums of $\alpha_i$.

    Furthermore, $f(w) = P(\seqof{\card[a]{w}}{a \in \Sigma})$,
    hence we can identify coefficients.
    \textbf{TODO: this has positive maximal coefficients}.
    Furthermore, this remains true when restricting the language.
\end{proof}

@@

\section{Deciding commutative $\Nat$-polyregular functions}
\label{sec:deciding}

decide nat inside rel in the commutative input case.

@@

\begin{corollary}
    The following problem is decidable: given $P \in \Rel[\vec{X}]$,
    decide whether $P$ is a \kl{$\Nat$-rational polynomial}.
\end{corollary}
\begin{proof}
    Thanks to \cref{karh:thm}, one only has to decide whether
    $P \in \CoveredPoly$. The procedure is as follows.
    \begin{enumerate}
        \item Check if all \kl{maximal monomials} have
            \kl{positive coefficients} in $P$, if not, answer \texttt{false}.
        \item Consider $N \in \Nat$ large enough so that
              $P \geq 0$ when all indeterminate are chosen greater
              than $N$. This is possible because all \kl{maximal
              monomials} have \kl{positive coefficients}, and such an $N$
              is computable.
        \item Compute $P$
    \end{enumerate}

    Now, if all \kl{maximal monomials}
    have \kl{positive coefficients}, then there exists a computable
    $N \in \Nat$ such that 
    In particular,

\end{proof}
